Preprocessing_&_Plot_for_Moral_Categ_Replication

### 2018-07-17 Replication/Results/dataAnalysis/preproc/MS_rep_prepro.rmd
change folder name

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.C1.V.sum_w,'MS_rep_categ_behav_wide.csv',row.names = F)
write.csv(df.C1.V.sum_noTask_w,'MS_rep_categ_behav_noTask_wide.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_l,'MS_rep_categ__rt_acc_long.csv',row.names = F)
write.csv(df.v.sum_eff_all_w,'MS_cross_taskeffect_wide.csv',row.names = F)
setwd(curDir)
```

>>>>

# write files to an upper-lelel folder
setwd(traDir)
write.csv(df.C1.V.sum_w,'MS_rep_categ_behav_wide.csv',row.names = F)
write.csv(df.C1.V.sum_noTask_w,'MS_rep_categ_behav_noTask_wide.csv',row.names = F)
write.csv(df.C1.V.sum_rt_acc_l,'MS_rep_categ__rt_acc_long.csv',row.names = F)
write.csv(df.v.sum_eff_all_w,'MS_rep_cross_taskeffect_wide.csv',row.names = F)
setwd(curDir)
```
